---
title: "Project report"
author: "Jan Sifrer"
date: "16. 5. 2022"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include=FALSE, echo=FALSE}
library(readr)
library(dplyr)
library(stringr)
library(knitr)
library(DT)

Grouped <- read_csv("Data/Grouped.csv")
Grouped_el <- read.csv("Data/Grouped_el.csv")
```

# Which elements most often congested the power grid? 

First, let's see who congested more than 10 times:
```{r, echo=FALSE}
#First, let's see who congested more than 10 times:
firs_one <- Grouped_el[Grouped_el$Sum > 10,][c(2,1,3)]
renderDataTable(firs_one)
```
**INTERPRETATIONS:**

* Westtirol Transformer WTRHU41 [DIR] was congested 136 times in this period.
* The German-Austrian power grid was congested for 281 times by Pleinting - St. Peter 258 [DIR] [AT].


Second, let's see who congested more than 2 times, but less than 10 times:
```{r, echo=FALSE}
#Second, let's see who congested more than 2 times, but less than 10 times:
second <- Grouped_el[Grouped_el$Sum > 2 & Grouped_el$Sum <= 10,][c(2,1,3)]
renderDataTable(second)
```

And now let see who congested less than 2 times:
```{r, echo=FALSE}
#And now let see who congested less than 2 times:
third <- Grouped_el[Grouped_el$Sum <= 2,][c(2,1,3)]
renderDataTable(third)
```

**Conclusion:**

In the first table, we can see, which elements congested the power grid more than 10 times. We can also see, that all these elements are part of Austrian, German, Netherlands, or Belgium power grid.

The second table shows which elements congested the power grid more than 2 times, but less than 10 times. They are part of Belgium, France, Netherlands, German, and Austria power grids.

And in the last table, we can see, which elements congested the power grid at least once, but less than 2 times. 

# Which power grid was congested most often? 

The table below shows us, how many times was some power grid congested. (Let's see those, who were congested more than 20 times).
We see that the German-Austrian power grid was congested the most. And the next problematic power grid was the German power grid.
```{r, echo=FALSE}
grouped2 <- Grouped[Grouped$Sum > 20,]
renderDataTable(grouped2)
```

# Model 

The application below, we can use for predictions. 
On the left side, we can choose the values for parameters, and on the right side, we get a table, which says what is approximated c-value and then is given a prediction interval. In the last column, we calculate the difference, if this difference is too small then the power grid would be congested. In the next row, we can see the probability that chosen power grid at a chosen time is congested.

If there are no graphs, change some parameters.

```{r, include=FALSE, echo=FALSE}
# source("Shiny/shiny.r", encoding = "UTF-8")

#source("library.r", encoding="UTF-8")

library(shiny)
library(shinythemes)
library(readr)
library(dplyr)
library(stringr)
library(lme4)
library(knitr)
library(DT)

# Load data
trend_data <- read_csv("Data/koef.csv",col_types = cols(Time = col_character()))

# Define UI
ui <- fluidPage(theme = shinytheme("united"),
                sidebarLayout(
                  sidebarPanel(
                    
                    # Select type of trend to plot
                    selectInput(inputId = "name2", label = strong("Name of the Power Grid"),
                                choices = unique(trend_data$Name2)[order(unique(trend_data$Name2))],
                                selected = "Diele - Meeden 380 Black [DIR] [DE]"),
                    
                    selectInput(inputId = "time", label = strong("Time"),
                                choices = unique(trend_data$Time),
                                selected = "00:00:00"),
                    
                    selectInput(inputId = "day", label = strong("Day of the week"),
                                choices = c(1:7),
                                selected = 1),
                    
                    numericInput(inputId = "AT", label = strong("PTDF for AT"),
                                 value = 0.58860, min = -1, max = 1, step = 0.00001),
                    
                    numericInput(inputId = "BE", label = strong("PTDF for BE"),
                                 value = 0.25637, min = -1, max = 1, step = 0.00001),
                    
                    numericInput(inputId = "DE", label = strong("PTDF for DE"),
                                 value = 0.58860, min = -1, max = 1, step = 0.00001),
                    
                    numericInput(inputId = "FR", label = strong("PTDF for FR"),
                                 value = 0.38150, min = -1, max = 1, step = 0.00001),
                    
                    numericInput(inputId = "NL", label = strong("PTDF for NL"),
                                 value = 0, min = -1, max = 1, step = 0.00001),
                    
                    numericInput(inputId = "ALBE", label = strong("PTDF for ALBE"),
                                 value = -0.30955, min = -1, max = 1, step = 0.00001),
                    
                    numericInput(inputId = "ALDE", label = strong("PTDF for ALDE"),
                                 value = 0, min = -1, max = 1, step = 0.00001),
                    
                    numericInput(inputId = "RAM", label = strong("RAM"),
                                 value = 1399, min = 0, max = 99999, step = 0.01),
                    
                    
                  ),
                  
                  # Output: Description, lineplot, and reference
                  mainPanel(
                    tableOutput("table"),
                    tableOutput("prob"),
                    plotOutput(outputId = "lineplot", height = "300px"),
                    plotOutput(outputId = "lineplot1", height = "300px")
                  )
                )
)

# Define server function
server <- function(input, output) {
  
  # Create scatterplot object the plotOutput function is expecting
  hh2 <- lmer(c ~ AT + BE + DE + FR + NL + ALBE + ALDE + RAM + (1|Name2/Day) + (1|Name2/Time), data = trend_data)
  
  output$lineplot <- renderPlot({
    trend_data1 <- trend_data[trend_data$Name2==input$name2,]
    trend_data1 <- trend_data1[trend_data1$Time==input$time,]
    trend_data1 <- trend_data1[trend_data1$Day==input$day,]
    #print(trend_data1$c)
        out <- tryCatch(
      {
        hist(trend_data1$difference, breaks=60, main="Histogram of Diference = RAM-c", xlab="Difference")
      },
      error=function(cond) {
        return("For this parameters I can not plot a histogram.")
      }
    )
    out
  })
  
  output$lineplot1 <- renderPlot({
    trend_data1 <- trend_data[trend_data$Name2==input$name2,]
    trend_data1 <- trend_data1[trend_data1$Time==input$time,]
    trend_data1 <- trend_data1[trend_data1$Day==input$day,]
    #print(trend_data1$c)
    out <- tryCatch(
      {
        plot(density(trend_data1$difference), main="Density of Diference = RAM-c", xlab="Difference")
      },
      error=function(cond) {
        return("For this parameters I can not plot a density function.")
      }
    )
    out
  })
  
    output$prob <-  renderTable({
        trend_data1 <- trend_data[trend_data$Name2==input$name2,]
        trend_data1 <- trend_data1[trend_data1$Time==input$time,]
        trend_data1 <- trend_data1[trend_data1$Day==input$day,]
        prob <- (sum(trend_data1$congested))/dim(trend_data1)[1]
        hh = data.frame("Probability" = prob)
  }, digits = 5)

  # Pull in description of trend
  output$table <-  renderTable({
    trend_data1 <- trend_data[trend_data$Name2==input$name2,]
    trend_data1 <- trend_data1[trend_data1$Time==input$time,]
    trend_data1 <- trend_data1[trend_data1$Day==input$day,]
    
    PTDF <- data.frame("Day"=input$day,"Name2"=input$name2, "Time"=input$time, "AT"=input$AT, "BE"=input$BE, "DE"=input$DE, "FR"=input$FR, "NL"=input$NL, "ALBE"=input$ALBE, "ALDE"=input$ALDE, "RAM"=input$RAM)
    #print(trend_data1[c(11,12,13,15,26)])
    out <- tryCatch(
      {
        v = predict(hh2,PTDF)
      },
      error=function(cond) {
        return(0)
      }
    )
    interval <- c(out - 1.96*sigma(hh2), out + 1.96*sigma(hh2))
    if (out == 0){hh = data.frame("ERROR" = "Change some parameters!")}
    else{
      hh = data.frame("Low boundary" = interval[1], "c" = out, "High boundary" = interval[2], "RAM" = input$RAM, "Difference" = input$RAM - out)}
  })
}
```

```{r, echo=FALSE}
# Create Shiny object
shinyApp(ui = ui, server = server)
#1+1
```
